Corpus

### 2020-05-15 evaluation/R/corpus.Rmd
Add additional data to corpus

@@

```{r load functions}
pkgs_functions <- 
  read_csv(
    PACKAGE_FUNCTIONS,
    col_types=cols(
      package = col_character(),
      fun = col_character(),
      num_params = col_double(),
      has_elipsis = col_logical(),
      exported = col_logical()
    )
  ) %>%
  count(package, exported) %>%
  mutate(type=ifelse(exported, "funs_public", "funs_private")) %>%
  select(-exported) %>%
  spread(key=type, value=n, fill=0) %>%
  mutate(funs=funs_public+funs_private)
```

@@

pkgs_revdeps <- count(pkgs_revdeps_raw, package) %>% rename(revdeps=n)
```

@@

```{r runtime checks}
pkgs_asserts <- 
  read_csv(
    PACKAGE_ASSERTS,
    col_types=cols(
      package = col_character(),
      fun_name = col_character(),
      file = col_character(),
      line1 = col_double(),
      col1 = col_double(),
      line2 = col_double(),
      col2 = col_double(),
      assert = col_character(),
      args = col_character()
    )
  ) %>%
  count(package, fun_name) %>%
  group_by(package) %>%
  summarise(funs_with_assert=length(unique(fun_name)), asserts=sum(n))
```

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```

>>>>

#### Coverage details

We have to manually add the header to the `coverage-details.csv` files.

```{r process package coverage details}
read_coverage_details <- function(file, package) {
  read_csv(
    file, 
    col_names = c( 
      "type",
      "filename",
      "functions",
      "first_line",
      "first_byte",
      "last_line",
      "last_byte",
      "first_column",
      "last_column",
      "first_parsed",
      "last_parsed",
      "value"
    ),
    col_types=cols(
      type = col_character(),
      filename = col_character(),
      functions = col_character(),
      first_line = col_integer(),
      first_byte = col_integer(),
      last_line = col_integer(),
      last_byte = col_integer(),
      first_column = col_integer(),
      last_column = col_integer(),
      first_parsed = col_integer(),
      last_parsed = col_integer(),
      value = col_double() # some value seems to be too big to fit into an int
    )
  ) %>%
    add_column(package, .before="type") %>%
    rename(fun=functions)
}

if (file_exists(PACKAGE_COVERAGE_DETAILS)) {
  coverage_details <- read_csv(
    PACKAGE_COVERAGE_DETAILS,
    col_types=cols(
      package = col_character(),
      type = col_character(),
      filename = col_character(),
      fun = col_character(),
      first_line = col_double(),
      first_byte = col_double(),
      last_line = col_double(),
      last_byte = col_double(),
      first_column = col_double(),
      last_column = col_double(),
      first_parsed = col_double(),
      last_parsed = col_double(),
      value = col_double()
    )
  )
} else {
  coverage_details_files <- path(PACKAGE_COVERAGE_DIR, pkgs_coverage$package, "coverage-details.csv")
  names(coverage_details_files) <- pkgs_coverage$package

  stopifnot(all(file_exists(coverage_details_files)))

  coverage_details <- imap_dfr(coverage_details_files, read_coverage_details)
  write_csv(coverage_details, PACKAGE_COVERAGE_DETAILS)
}
```

```{r function coverage}
coverage_funs <- 
  coverage_details %>%
  filter(type=="all") %>%
  group_by(package, fun) %>%
  summarise(coverage=ifelse(n() > 0, sum(value > 0)/n(), NA))

write_csv(coverage_funs, CRAN_COVERAGE_FUNCTIONS)
```

@@

```{r load functions}
pkgs_functions_raw <- 
  read_csv(
    PACKAGE_FUNCTIONS,
    col_types=cols(
      package = col_character(),
      fun = col_character(),
      exported = col_logical(),
      is_s3_dispatch = col_logical(),
      is_s3_method = col_logical(),
      params = col_character()
    )
  )

pkgs_functions_exported <-
  pkgs_functions_raw %>%
  count(package, exported) %>%
  mutate(exported=ifelse(exported, "funs_public", "funs_private")) %>%
  pivot_wider(
    names_from=exported, 
    values_from=n, 
    values_fill=list(n=0)
  )

pkgs_functions_s3 <-
  pkgs_functions_raw %>%
  group_by(package) %>%
  summarise(funs_s3_dispatch=sum(is_s3_dispatch), funs_s3_method=sum(is_s3_method))

pkgs_functions <-
  pkgs_functions_exported %>%
  left_join(pkgs_functions_s3, by="package") %>%
  mutate(
    funs_s3_dispatch=replace_na(funs_s3_dispatch, 0),
    funs_s3_method=replace_na(funs_s3_method, 0),
    funs=funs_public+funs_private,
    funs_s3=funs_s3_dispatch+funs_s3_method
  )
```

### Package classes

```{r load classes}
pkgs_classes_raw <- 
  read_csv(
    PACKAGE_CLASSES,
    col_types=cols(
      package = col_character(),
      class = col_character()
    )
  )

pkgs_classes <- 
  select(pkgs_loadable, package) %>%
  left_join(count(pkgs_classes_raw, package), by="package") %>% 
  rename(s3_classes=n) %>%
  mutate(s3_classes=replace_na(s3_classes, 0))  
```

@@

pkgs_revdeps <- 
  pkgs_revdeps_raw %>%
  left_join(select(pkgs_runnable_code, package, runnable_code), by=c("revdep"="package")) %>%
  group_by(package) %>%
  summarise(revdeps=n(), revdeps_runnable_code=sum(runnable_code, na.rm=T))
```

@@

```{r runtime checks}
pkgs_asserts_raw <-
  read_csv(
    PACKAGE_ASSERTS,
    col_types=cols(
      package = col_character(),
      fun_name = col_character(),
      file = col_character(),
      line1 = col_double(),
      col1 = col_double(),
      line2 = col_double(),
      col2 = col_double(),
      assert = col_character(),
      args = col_character()
    )
  )
write_csv(pkgs_asserts_raw, CRAN_ASSERTS)

pkgs_asserts <- 
  pkgs_asserts_raw %>%
  count(package, fun_name) %>%
  group_by(package) %>%
  summarise(funs_with_assert=length(unique(fun_name)), asserts=sum(n))
```

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_classes, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```
